Pool Model

### 2023-12-20 pool_model.tex
explain implementation of lag phase in abm

>>>>

In addition to modeling division events, the cells have are subject to the lag-phase which delays their ability to proliferate.
We model this by assigning a transition rate to each cell.
For each time point of the simulation, we generate a boolean value from a random number generator with probability
    P(\text{transition}) = \Delta t \lambda \frac{[R]}{[R_0]}.
If this boolean is true, we move the cell from the inactive state to the active state where it starts to consume nutrients and grow.
It is clear that this is exactly identical to the \ac{ode} model.
